---
title: "Assignment 2 Task 1"
author: "Amelia Ritger"
date: "3/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message=FALSE,
                      warning=FALSE)
```

You have a number of tools in your multivariate analysis & exploration toolbelt, like:
Multiple linear regression
Correlation matrices
Principal components analysis
K-means clustering
Hierarchical clustering

For Task 1, you should explore, analyze and visualize a multivariate dataset using at least 3 of the methods listed above (more if you feel inspired). Prepare your analysis and findings in a single knitted HTML that can be featured as a project to highlight your data analysis and coding skills (e.g. on your personal website). The analysis should provide a short introduction, clear subsections and descriptions, and insights/summaries of relationships between variables and between groups. 

The dataset we recommend using for this task: Santa Barbara stream water chemistry for registered streams, collected as part of the Santa Barbara Coastal Long Term Ecological Research Program (SBC LTER). Link to the data: https://drive.google.com/file/d/16rYLBi-CgvjcWhOsX1SLdD9HHUMP9m2l/view?usp=sharing

DATA & METADATA SOURCE: 
SBC LTER: Stream chemistry in the Santa Barbara Coastal drainage area, ongoing since 2000
Creators: Santa Barbara Coastal LTER, & Melack, John M
Citation: Santa Barbara Coastal LTER and J. Melack. 2019. SBC LTER: Land: Stream chemistry in the Santa Barbara Coastal drainage area, ongoing since 2000 ver 16. Environmental Data Initiative. https://doi.org/10.6073/pasta/67a558a24ceed9a0a5bf5e46ab841174. 

You can decide which variables and observations you want to explore/include. For example: You might narrow the data to just a few sites of interest, or only include complete cases (with no NAs) for cluster analyses. Hint: if you’re doing hierarchical clustering by site, you’ll want to make a data frame that has a single summary row per site (e.g. based on means from all observations at that site), then calculate the euclidean distance. 

Note/warning: You are welcome to use a different dataset if you have that is more interesting to you, but we may not be able to easily troubleshoot if you do. 

Load packages and data
```{r}
library(tidyverse)
library(janitor)

water <- read_csv("sbc_lter_registered_stream_chemistry.csv") %>% 
  clean_names()



```

